\documentclass[
    nolot,
    color,   % Enables colorful typesetting. Replace with
             % `monochrome`, if you are going to print the
             % thesis on a monochromatic printer.
	table,   % Causes the coloring of tables. Replace with
             % `notable` to restore plain tables.
    oneside, % Enables double-sided typesetting. Replace
             % with `twoside`, if you are going to print
             % your thesis on only one side of the paper.
    % More options are listed in the class documentation
    % available at <https://www.ctan.org/pkg/fithesis>.
]{fithesis3}
\bibliographystyle{plain}
\usepackage[english]{babel} % By using `czech` or `slovak`
% instead of `english`, you can typeset the entire thesis
% in either Czech or Slovak, respectively. Changing the
% language requires a clean compilation; click `recompile
% from scratch`, when Overleaf raises an error.
\usepackage{import}
\thesissetup{
	university    = mu,
	faculty       = fi,
    type          = mgr,
    author        = Bc. Linda Hansliková,
    gender        = f,
    advisor       = {RNDr. Martin Stehlík, Ph.D.},
    title         = {The Categorization of the Darkweb},
    TeXtitle      = {The Categorization of the Darkweb},
    keywords      = {Web Application, Dark-web, Python, RestApi, Django REST, TypeScript, React, Redux, d3 Graph},
    TeXkeywords   = {dark web, artificial neural networks, supervised learning, community detection, web graph, web application},
    assignment    = {}
}
\thesislong{abstract}{	
	The ordinarily accessible online world is composed of commonly legal, interlinked sites and pages. The structure of the dark web, however, may be different because of the nature of this hidden part of the Internet. Questions about the interconnection and the categorical makeup of the dark web content arise. 

We were interested in answering these questions for a portion of the dark web. The results of our work include a classification model which categorizes the dark web pages with an accuracy of 88.2\%. We compared two community detection algorithms and determined the Leiden algorithm to be more suited for the fulfilling of our goal. We visualized the pages divided into communities in form of a web graph. 

The final web application is to our knowledge, at the time of writing this thesis, the only publicly available software to categorize the dark web content, display a comprehensible and zoomable web graph with information about category makeup, and the option of downloading further page details.

}
\thesislong{thanks}{
	My thanks go to my adviser RNDr. Martin Stehlík, Ph.D. for allowing me to proceed with this topic, for his guidance, invaluable advice, and patience. I thank Matej Pavla for his emotional support and for motivating me. I am also thankful to Jozef Vilkolák for the mathematical advice he has given me.

}

% The beginning of the document
\usepackage{amsmath}
\usepackage{tabularx}
\usepackage{booktabs}
\usepackage{wrapfig}
\usepackage{sidecap}
\usepackage[toc,page]{appendix}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{listings}
\usepackage{placeins}
\usepackage{flafter} 
\usepackage{float}
\usepackage{placeins}
\usepackage{adjustbox}

\lstdefinestyle{sharpc}{language=[Sharp]C, basicstyle=\ttfamily\footnotesize, breaklines=true}
\sidecaptionvpos{figure}{c}

\begin{document}
  \pagestyle{plain}
  
\setlength\emergencystretch{3cm}
  \chapter{Introduction}
  \import{chapters/}{introduction.tex}
  \chapter{Data set analysis}
  \import{chapters/}{datasetAnalysis.tex}
  \chapter{Classification}
  \import{chapters/}{classification.tex}
  \chapter{Clustering}
  \import{chapters/}{clustering.tex}
  \chapter{Development}\chaptermark{Development}
  \import{chapters/}{development.tex}  
  \chapter{Evaluation}
  \import{chapters/}{evaluation.tex}  
  \chapter{Conclusion}
  \import{chapters/}{conclusion.tex}
   \bibliography{bib_file}{}
  \import{chapters/}{appendix.tex}
\end{document}
